\section{Design}
The design of the simulator was made with 3 main objectives.
\begin{itemize}
    \item Extensibility
    \item Simplicity
    \item Testability
\end{itemize}


\subsection{Extensibility}
Although extensions was not planned for the simulator from the beginning.
Having some degree of maintainability and extensibility is relevant for this project, as with more time, the simulator would be extended with more instruction sets.
To facilitate this design, code is split by their domains, like for example: 
Branch operations, Logical operations, Arithmetic operations, Memory operations, Decoding, Opscodes mapping, Binary handling, Tests, etc...

\subsection{Simplicity}
With a limited timeframe comes a limited scope. To combat potential scope creep, simplicity was choosen any time over cool or fancy stuff.
The risk of not getting the minimal viable solution ready before deadline was too likely and consequential, if cool and fancy alleyways are visited first time around.
It could be cool to boot linux, extend with all extensions (RS64I, RS32M, ...) or staged pipeline.
But for this simulator, the simplest approach was taken until a more advanced approach was absolutely neccesary.

\subsection{Testability}
In an attempt to increase development speed and correctness, the simulator was built with high testability in mind.
Initialy tests were concieved such that a full instruction in the form of an integer is given, executed with assertions on the side effects.
Although pretty granular, it was still testing too much at once with both the operation and the encoding.
Another drawback of the initial approach, is that specifying integers as instructions for test cases is not very readable, and require intimate knowledge of the system.

To enable simpler tests of operations, simpler function declarations would be needed, like for example: $$add(rd, rs1, rs2)$$
This way, a very readable and simple test could be constructed like the following: \label{test}
$$ a_1 \leftarrow 5 $$
$$ a_2 \leftarrow 3 $$
$$ add(a_0, a_1, a_2) $$
$$ \textbf{assert } a_0 = 8 $$

A looser coupling, like with the decoupling of decoding and operations, will make the simulator more testable. 
The looser coupling also as a bonus result make the code more readable.
This pattern is extended to all parts of the simulator, such that functions are limited to a singular responsibility which makes them easier to read, determine behavior, code and test.